### 2020-11-10 treatise/abstract.tex
Delete obsolete formulation on SOCP

Multiple-input-multiple-output (MIMO) is the next-generation standard of wireless communication.
While the channel state information has to be known at the receiver for communication algorithms, for MIMO system the estimation is not easy.
Meanwhile, the millimeter wave (mm-Wave) band, often used together with MIMO, is known to exhibit sparsity, and results on compressive sensing suggest that sparsity implies that fewer channel measurements shall suffice.
In practice, Orthogonal Matching Pursuit (OMP) is usually used, as it has lower complexity.

It is interesting to note that Dantzig Selector (DS), proposed by Tao and Candès, has seldom been applied.
DS has several promising properties, and it is worthwhile to investigate how it performs on the channel sensing problem.
In this treatise, we consider a mm-Wave MIMO channel, and a hybrid structure at both the transmitter and receiver end.
Using pilot signal and predetermind random beamformer, we apply DS for channel estimation, arguing in favor of its greater generality, its tolerance of noise corruption, and its lower averaged error.
The treatise also gives a bound for the expected square error of DS, as well as bounded probability of success, and in so doing, showing dependency on the number of path and channel sparsity.

DS can be cast as a linear program (LP), so that known methods for convex programs may be applied.
Simulation is done on DS and other methods, and we discuss their respective merits.
It turns out DS is steadily better than other alternatives, while it has siginificantly greater complexity.

>>>>

Multiple-input-multiple-output (MIMO) is the future of wireless communication, but the large number of antennae makes it difficult to estimate its channel state information.
Since millimeter wave (mm-Wave) band, often used together with MIMO, is known to exhibit sparsity, results on compressive sensing suggest that, on mm-Wave band, fewer channel measurements shall suffice.
Current literature prefers orthogonal matching pursuit (OMP) due to its lower complexity.
It is interesting to note that Dantzig Selector (DS), claimed to have various performance guarantee, has seldom been examined.

In this treatise, we consider a mm-Wave MIMO channel, and a hybrid structure at both the transmitter and receiver end.
Using pilot signal and 
We demonstrate that DS can be applied on a entrywise i.i.d.\ random beamformer, and give a bound for its expected error norm, which holds for high probability.
DS is cast as a linear program, and simulation is done.
We argue that DS is steadily better in our configuration, while it has siginificantly greater complexity.

### 2020-11-10 treatise/conclusion.tex
Delete obsolete formulation on SOCP

This treatise studied the effective estimation of the millimeter wave, multiple-input, multiple-output (mm-wave MIMO) channel.
We adopts the Dantzig Selector (DS) rather than Orthogonal Matching Pursuit (OMP), which is most commonly used in literature, as the estimation algorithm, therefore exploiting the sparsity of the problem in spacial Fourier domain.
We bounded the expected square error following the spirit of Candès and Tao \cite [CaT07].
Towards that end, we characterized the spacial sparsity, confirmed the restricted isometry of measurement matrix \m {\M {P}}, and justified the generalization for complex vectors.
The bound assumes a fairly general setting, and is expressed in terms of physical parameters, such as the number of path \m {L} and channel dimension \m {N_H}.

Simulation is done, and DS's performance is compared to OMP, Lasso, and LS.
DS performs slightly better than others, but gives much higher complexity, agreeing our analysis.
Put concisely, no algorithm is a universal solution, as they trade off precision for time and space complexity, or conversely, among other things.
We hope that our inquiry of DS suggests a welcomed alternative added to the present literature of channel estimation.

>>>>

This treatise investigates effective estimation of the millimeter wave, multiple-input, multiple-output (mm-wave MIMO) channel.
We adopt the Dantzig Selector (DS) rather than Orthogonal Matching Pursuit (OMP), which is most commonly used in literature, by exploiting the sparsity of the problem in spacial Fourier domain.
We bounded the expected error norm following the spirit of Candès and Tao \cite [CaT07].
To do so, we evaluate the sparsity, confirm the restricted isometry of sensing matrix \m {\M {P}}, and generalize the method for complex vectors.
Our bound, on a general setting, is characterize in terms of physical parameters, such as the number of path \m {L} and channel dimension \m {N_H}.
Simulation is done, and DS's performance is compared to OMP, Lasso, and LS.
DS outperforms others, at the cost of higher complexity, agreeing our analysis.
Put concisely, DS trades off time and space complexity for precision, and we hope that our inquiry provides a welcome alternative to the present literature.
